A Detection of the Environmental Dependence of the Stellar Profiles and haloes of Massive Central Galaxies

### 2017-07-13 draft/paper2.tex
Edit result 4

    In the last section, we show that the median \mden{} profiles of massive central 
    galaxies depend on environment. 
    Therefore, we expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
    relations of the \rbcg{} and \nbcg{} samples. 
    For this purpose, we still use \mtot{} as proxy of ``total'' \mstar{}, and adopt 
    the radius enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived 
    from the $i$-band curve-of-growth) as ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction. 
    Massive galaxies from this sample are large enough so we do not need to worry 
    about the effects of seeing.

@@

    We qualitatively compare our results with \citealt{HCompany13} (HC13; green solid line) 
    who studied $z\leq 0.09$ central ETGs in $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{} and  
    empirically convert the \mstar{} from a Kroupa IMF to a Chabrier IMF by applying 
    a constant -0.05 shift (see \citealt{Bernardi2016}).
    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We add $+0.1$dex to the HSC13 \mstar{} to account for the systematic 
    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
    The distributions of both \rbcg{} and \nbcg{} galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes) even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies from $12.5\le$ \logmh{} $<15.0$ haloes.
    A possible explanation for this difference is that the region that strongly depends 
    on halo mass is the low surface brightness outer envelope where the stars are 
    mostly assembled through multiple mergers. 
    This region is difficult to detect on shallow SDSS images, but the much deeper 
    HSC images can provide accurate measurements of total \mstar{} and size.

    In conclusion, we confirm that massive central galaxies at $0.3 < z < 0.5$
    follow \mtot{}--$R_{\mathrm{50}}$ relations that show halo mass dependence. 
    At fixed \mtot{}, massive central galaxies in denser environment (higher \mhalo{}) 
    have slightly larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
    \mtot{}. 
%% ------------------------------------------------------------------------------------ %%

@@

    We also investigate the relationship between \mstar{} for two different
    fixed physical apertures (\mtot{} v.s. \minn{}) as alternative tool to help us 
    understand the relationship between \mhalo{} and the assembly history of massive
    galaxies.   
    Comparing to the mass-size relation, this relation is not affected by the 
    ambiguous definition of ``size'', and is much easier to apply to larger samples 
    and to simulations.

    The right panel of Fig \ref{fig:scaling_relation} compares \mtot{} and \minn{}. 
    We find that our \rbcg{} and \nbcg{} occupy different locations within this plane,
    and follow different best-fit \mtot{} - \minn{} relations. 
    For \rbcg{} galaxies we find:

@@

    We have checked that our results are unchanged if we replace the \minn{} with 
    \mstar{} within 5 or 15 kpc apertures. 
    Although the $M_{\star, 5\ \mathrm{kpc}}$ values are less reliable than \minn{} 
    due to the impacts of seeing, the relation using $M_{\star, 5\ \mathrm{kpc}}$ shows 
    more significant \mhalo{} dependence at the high-mass end.
    Also, best-fit relation using the full \mtot{} range results in even shallower 
    slope for the \rbcg{} galaxies.

    Our results suggest that: 
    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
    lower fractions of \mstar{} stored in the inner region; 
    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
    average have more prominent outer envelopes. 
    The scientific implication of this result is briefly discussed in 
    Section~\ref{sec:discussion}.

    At the same time, we also find \rbcg{} galaxy tends to have lower \mstar{} within 
    inner 5-10 kpc and shallower inner \mden{} profile than the \nbcg{} one at 
    fixed \mtot{}. 
    Although the HSC images do not have sufficient resolution to investigate this in 
    details, it is worth pointing out that this difference could be physically 
    interesting. 
    Observations of compact quiescent galaxies at high-$z$ often reveal higher 
    \mden{} in the central region than their descendants, and certain process need to  
    be responsible for reducing the central \mden{} (e.g. strong adiabatic expansion 
    induced by powerful AGN feedback; \citealt{Fan2008}).
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
    common in the assembly history of massive galaxies, can also flatten the central 
    \mden{} profile (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
    problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.
%% ------------------------------------------------------------------------------------ %%

>>>>

    In the last section, we show that the median \mden{} profiles of massive central 
    galaxies depend on environment. 
    We therefore expect to also see difference in the \mstar{}--$R_{\mathrm{e}}$ 
    relations of the \rbcg{} and \nbcg{} samples. 
    For this purpose, we still use \mtot{} as proxy of ``total'' \mstar{}, and adopt 
    the radius enclosing 50\% of luminosity within 100 kpc ($R_{\mathrm{50}}$; derived 
    from the $i$-band curve-of-growth) as ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction. 
    Massive galaxies from this sample are large enough so we do not need to worry 
    about the effects of seeing.

@@

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 uses the group catalog by \citet{Yang2007} to estimate \mhalo{}. 
    They estimate the 2-D $R_{\mathrm{e}}$ using single-\ser{} model fitting to SDSS 
    images, and derived \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    The \mstar{} estimates are empirically converted from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 shift (see \citealt{Bernardi2016}).
    We add $+0.1$dex to the HSC13 \mstar{} to account for the systematic 
    difference between their BC03 and our FSPS model (see Appendix~\ref{app:sed}). 
    The distributions of both \rbcg{} and \nbcg{} galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies from $12.5\le$ \logmh{} $<15.0$ haloes.
    The \mstar{} and $R_{\mathrm{e}}$ in HC13 are based on much shallower SDSS images
    that can not constrain the environment-sensitive outer stellar halos well. 
    Detailed analysis on this topic is beyond the scope of this work, but we briefly 
    demonstrate this using the \rbcg{} and \nbcg{} galaxies that overlap with the GAMA
    survey (please see Appendix~\ref{app:gama} for details). 
    We matched the two samples using the \mstar{} measured using single-\ser{} 2-D
    model by the GAMA team (\citealt{Kelvin2012}). 
    At fixed \mgama{}, the \rbcg{} galaxies display much more significant stellar 
    halo despite they have very similar inner \mden{} profiles.  
    This shows again that the deeper HSC images has unique advantage in studying the
    connection between the assembly of massive galaxies and their dark matter haloes.

    In conclusion, we confirm that the \mtot{}--$R_{\mathrm{50}}$ relation of massive
    central galaxies at $0.3 < z < 0.5$ depends on halo mass. 
    At fixed \mtot{}, massive central galaxies in denser environment (higher \mhalo{}) 
    have slightly larger $R_{\mathrm{50}}$ comparing to ones in smaller haloes at fixed 
    \mtot{}. 
%% ------------------------------------------------------------------------------------ %%

@@

    Now we investigate the relationship between \mstar{} within two elliptical 
    apertures (\mtot{} v.s. \minn{}) as alternative tool to help us explore the 
    structure and assembly of massive galaxies.
    Comparing to the mass--size relation, this relation is not affected by the 
    ambiguous definition of ``size'', and it is easier to apply it to larger 
    samples or numerical simulations.

    The right panel of Fig \ref{fig:scaling_relation} compares the \rbcg{} and \nbcg{}
    galaxies on the \mtot{}--\minn{} plane.
    We show that these two samples occupy slightly different locations on this plane,
    and follow different best--fit \mtot{}--\minn{} relations. 
    For \rbcg{} galaxies with \logmtot{}$>11.6$ we find:

@@

    These results are robust against the \mtot{} range for fitting, and they will not 
    be affected if we replace the \minn{} with \mstar{} within 5 or 15 kpc apertures
    or replace the \mtot{} with \mstar{} within 120 or 150 kpc apertures.  
    The \mtot{}--$M_{\star, 5\ \mathrm{kpc}}$ relation actually suggests clearer 
    \mhalo{}-dependence at high-\mtot{} end, but the $M_{\star, 5\ \mathrm{kpc}}$ 
    are more vulnerable to the impact from seeing than \minn{}.

    We conclude that: 
    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
    lower fractions of \mstar{} stored in the inner region; 
    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
    average have more prominent outer envelopes. 
    The scientific implication of this result is briefly discussed in 
    Section~\ref{sec:discussion}.

    Meanwhile, we find \rbcg{} galaxy tends to have lower \mstar{} within 10--15 kpc 
    and shallower inner \mden{} profile than the \nbcg{} one at fixed \mtot{}. 
    Although the HSC can not resolve the central region of these massive galaxies, 
    such difference could have interesting physical implications. 
    Observations of compact quiescent galaxies at high-$z$ tend to suggest higher 
    \mden{} in the central region than their descendants, hence it is necessary to 
    have certain process to reduce the central \mden{} (e.g. strong adiabatic expansion 
    induced by powerful AGN feedback; \citealt{Fan2008}) to match the inner \mden{} 
    profiles of massive central galaxies at low-$z$.
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
    common in the assembly history of massive galaxies, can also flatten the central 
    \mden{} profile via efficient scattering effect (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
    problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.
%% ------------------------------------------------------------------------------------ %%
